---
title: "p8105_hw1_yz3297"
author: "Yue Zhao"
date: "9/20/2018"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```



## Problem 1
This builds a data frame.
```{r}
example_df = tibble(
  vec_numeric = runif(10, min = 0 ,max = 5),
  
  vec_logical = (vec_numeric >= 2),
  
  vec_char = c("China", "Japan", "India", "US", "Korea", "France", "Germany", "Qatar", "Brazil", "England"),
  
  vec_factor = factor(c("Asia", "Asia", "Asia", "America", "Asia", "Europe", "Europe", "Asia", "America", "Europe"))
)
```



This takes the mean of the vectors.
The numeric and logical vectors works when I take the mean
```{r}
mean(example_df$vec_numeric)
mean(example_df$vec_logical)
```


The character and factor vectors do not work when I take the mean
```{r}
mean(example_df$vec_char)
mean(example_df$vec_factor)
```

This is because mean can only be calculated for numeric number and logical vector. 
Logical Vector works because true is taken as 1 and false is taken as 0.



Code Chunk for Converting Variable Type 1 (no output)
```{r eval = FALSE}
as.numeric(example_df$vec_logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
```

Converting from logical and factor to numeric is fine but converting character vector to numeric shows "NA".



Code Chunk for Converting Variable Type 2
```{r}
as.numeric(as.factor(example_df$vec_char))
as.numeric(as.character(example_df$vec_factor))
```

The first one works fine and the second one returns "NA".


## Problem 2

```{r}
example_df2 = tibble(
   x = rnorm(1000),
   y = rnorm(1000),
   vec_logical2 = (x + y > 0),
   vec_numeric2 = as.numeric(vec_logical2),
   vec_factor2 = as.factor(vec_logical2)
)
```

The size of the dataset is 
`r nrow(example_df2)`* `r ncol(example_df2)`.
The mean of x is `r mean(example_df2$x)` and the median of x is `r median(example_df2$x)`.

The proportion of cases for which the logical vector is True is `r as.numeric(example_df2$vec_logical2)`.
















You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
